\LARGE \bf ***

### 2020-09-21 icra-2021.tex
some changes in the introduction

@@

Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}. Although researchers have satisfied some of these demands applying mobile robots in applications such as harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, more complex monitoring strategies--often implemented utilizing unmanned aerial vehicles (UAVs)--are usually required for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}. Planning a mission for UAVs operating in such scenarios is a challenging task. It usually requires advanced levels of autonomy--with the UAV being required e.g., to inform its grounded counterparts of obstacles detected while flying--along with strictly limited energy budgets. The presented approach proposes a \emph{mission-aware energy planning algorithm} for UAVs for precision agriculture that addresses the broader problem of increasing \emph{computational demands} and their relation to the UAV's energy consumption and autonomy.

---

The energy is varied by means of mission-specific parameters, the Quality of Service (QoS) of the onboard computations, and the trajectory explicit equations (TEEs) parameters. The approach ideally accounts for a mission extension by adapting the QoS and TEEs parameters as the robot batteries drain.

The algorithm relies on the assumptions of the mission--a set of tasks the mobile robot is supposed to perform--being \emph{periodic} and \emph{uncertain}. The periodicity is directly observed by e.g., the mobile robot traveling in repetitive patterns executing a set of assigned tasks, and the uncertainty accounts for the environmental interference, with e.g., a fixed-wing craft drifting due to windy weather. The algorithm proposes a Fourier series to address the periodicity assumption--being the mission periodic, we expect the energy to evolve also periodically--and a state observer--a Kalman filter--to address the uncertainty assumption.

Energy planning algorithms for mobile robots are not a new concept and have been extensively studied in the literature, being these correlated to such topics as trajectory generation and path planning. Generally, they account for the energy due to the trajectory, by e.g., maximizing the operation time~\cite{wahab2015energy}, but practically restrict to a specific class of mobile robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}. In a similar setting, rotorcrafts have been an obvious object of research interest, with such approaches as the energy-efficient trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}. Conversely, the presented approach attempts to combine and generalize some of these technical breakthroughs and correlate the--extensively studied--energy planning to the growing computational demands through a mission-aware perspective.
Of particular inspiration to the approach is the technique of coupling the energy due to the computations performed and trajectory traveled, although being--likewise the others--limited to the trajectory~\cite{mei2004energy,mei2005case,mei2006deployment}, or to the class of mobile robots~\cite{sadrpour2013mission,sadrpour2013experimental}.

% [Ad:] I am actually thinking whenever I should put a section with problem statement or I can just leave it nicely in the model?

>>>>

  @inproceedings{daponte2019review,
    title={A review on the use of drones for precision agriculture},
    author={Daponte, Pasquale and De Vito, Luca and Glielmo, Luigi and Iannelli, Luigi and Liuzza, Davide and Picariello, Francesco and Silano, Giuseppe},
    booktitle={IOP Conference Series: Earth and Environmental Science},
    volume={275},
    pages={012022},
    organization={IOP Publishing}

@@

Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}. Researchers have fulfilled some of these demands applying mobile robots in agricultural applications such as harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, where complex monitoring strategies--often implemented utilizing unmanned aerial vehicles (UAVs)--are usually required for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}. Planning a mission for UAVs operating in such scenarios is a challenging task. It usually requires advanced levels of autonomy--with the UAV being, e.g., used to inform its grounded counterparts of obstacles detected while flying--along with strictly limited energy budgets. Currently, UAVs in precision agriculture use-cases are semi-autonomous, in the sense that the path is static and defined using a mission planning software~\cite{daponte2019review}. The presented approach proposes an \emph{energy-aware dynamic mission planning algorithm} for UAVs for precision agriculture that addresses the broader problem of increasing \emph{computational demands} and their relation to the UAV's energy consumption, path, and autonomy.

The energy is varied by means of mission-specific parameters, the Quality of Service (QoS) of the onboard computations, and the trajectory explicit equations (TEEs) parameters. The approach ideally accounts for a mission extension by adapting the QoS and TEEs as the UAV batteries drain. Preliminary data using a terrestrial fixed-wing UAV indicates a potential extension of up to 13 minutes over 1 hour by switching to the lowest QoS.

The algorithm relies on the assumptions of the mission--a path and a set of tasks the UAV is supposed to perform--being \emph{periodic} and \emph{uncertain}. The periodicity is directly observed, by e.g., the UAV flying in repetitive patterns, and the uncertainty accounts for the environmental interference with e.g., a fixed-wing UAV drifting due to windy weather. We propose the Fourier analysis to address the periodicity assumption--being the mission periodic, we expect the energy to evolve also periodically--and a state observer--a Kalman filter--to cope with the uncertainty assumption. The algorithm selects the controls--the QoS and TEEs--dynamically using a modified tube-based output model predictive control (MPC), which ensures that state estimation error does not result in transgression of the control and state constraints.

Although underrepresented in precision agriculture and related literature, energy planning algorithms for mobile robots are not a new concept and have been extensively studied in the literature, being these correlated to such topics as trajectory generation and path planning. Generally, they account for the energy due to the trajectory, by e.g., maximizing the operation time~\cite{wahab2015energy}, but practically restrict to a narrow class of mobile robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}. In a similar setting, rotorcrafts have been an obvious object of research interest, with such approaches as the energy-efficient trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}. Conversely, the presented approach attempts to combine and generalize some of these technical breakthroughs and correlate the--extensively studied--energy planning to the growing computational demands of precision agriculture UAVs through a mission-aware perspective.
Of particular inspiration to the approach is the technique of coupling the energy due to the computations performed and trajectory traveled, although being--likewise the others--limited to the trajectory~\cite{mei2004energy,mei2005case,mei2006deployment}, or to the class of mobile robots~\cite{sadrpour2013mission,sadrpour2013experimental}.
